Summary Tables

### 2019-04-29 summary_tables.Rmd

## Scenario definition
Table displays highest propensity for each distance category, for a given mode.

>>>>

## Scenario definition
Table displays highest propensity (%) for each distance category, for a given mode.

In scenario generation, trips are sampled without replacement to increase the share of the requested mode up to the total shown.

Distance categories are:

0-1 km = \{trip distance < 2\}

2-5 km = \{2 <= trip distance < 6\}

6+ km = \{6 <= trip distance\}
